\section{Search for Nash equilibrium}

\subsection{overview}
\begin{enumerate}
	\item Fixed Point theorem
			\begin{itemize}
				\item Kakutani (1941) theorem. Used by John Nash.
				
					  If the best response function $br$ is not set value function
				\item Banach fixed point theorem
				
						If the best response function is a strict contraction, then there is a unique fixed point.
				\item Brouder, Brower, Schauder fixed point theorem (used to show existence of a fixed point)
				\item special structure of the Game
						\begin{itemize}
							\item Tarski (unimodular game)
							\item potential game
						\end{itemize}
			\end{itemize}
	\item Variational Inequalities
			\begin{itemize}
				\item Graphon Games
			\end{itemize}
\end{enumerate}

\subsection{An example for Nash equilibrium}

Assume that $A^i = \mathbb{R}$ the real line. For each player $i \in \{1,\ldots,N\}$, We consider a cost function
$$
	J^{i}(\alpha^i, \alpha^{-i}) = f_i(\alpha^i - \alpha^{i,0} + \delta \cdot \sum_{j \neq i} a_{ij}^{(G)} \alpha^j ) + g_i(\alpha^{-i})
$$
where $\alpha^{i,0}$ is an (autistic) action preferred by player $i$. 

Assume that $f_i$ is symmetric and descending on $(-\infty, 0]$, and increasing on $[0, \infty)$.
	\begin{itemize}
		\item $f_i(x) = f_i(-x)$ for any $x \in \mathbb{R}$
		\item $f_i(0) = \min_x f_i(x)$
	\end{itemize}
For any $i \in \{1,\ldots,N \}$, if $\alpha^{-i}$ is given, the best response obtained for player $i$ is
\begin{equation}
	br^{i}(\alpha^{-i}) = \alpha^{i,0} - \delta\cdot \sum_{j \neq i} a_{ij}^{(G)} \cdot \alpha^j
\label{eq:best_response_player_i}
\end{equation}
A fixed point for the best response function will satisfy
$$
	\alpha^{i} = \alpha^{i,0} - \delta \cdot \sum_{j \neq i} a_{ij}^{(G)} \cdot \alpha^j
$$
Assume that $a_{ii}^{(G)} = 0$, we can have
$$
	\balpha = (\bI + \delta A^{G})^{-1} \cdot \balpha^0
$$
If the game is symmetric: $\alpha^{i,0} = \alpha^{0} \in \mathbb{R}$ for all $i \in \{1,\ldots, N\}$, then 
\begin{eqnarray}
	\balpha &=& \alpha^{0} \cdot (\bI + \delta A^{(G)})^{-1} \mathbbm{1} \nonumber \\
	&=&  \alpha^0 \left( \bI - [\bI _+ \delta A^{(G)}]^{-1} [\bI + \delta A^{(G)}] + [\bI + \delta A^{(G)}]^{-1} \right) \mathbbm{1} \nonumber \\
	&=& \alpha^0 (\bI - \delta [\bI + \delta A^{(G)}]^{-1} A^{(G)} ) \mathbbm{1} \nonumber \\
	&=& \alpha^0 ( \mathbbm{1} - \mathbbm{b}_{\delta, -\delta})
\end{eqnarray}
where $\mathbbm{b}_{a,b}$ is the Bonacich centrality measure.

\begin{remark}
In this example, we can see that the Nash equilibrium only depends on the graph structure (through the Bonacich centrality measure), bu not the functions $f_i$ nor $g_i$.
\end{remark}

\begin{remark}
We can have a more general setting for the action space $A^i$, for example:
\begin{itemize}
	\item if $A^{i} = [0, \infty)$, the Nash equilibrium becomes
		$$
			\alpha^{*,i} = \max \left\{0, \alpha^{i,0} - \delta \sum_{j \neq i} a_{ij}^{(G)} \alpha^{*,j} \right\};
		$$
	\item if $A^{i} = [0, L]$ for some $L>0$, the Nash equilibrium becomes
	$$
	\alpha^{*,i} = \min \left\{ L, \max \left\{0, \alpha^{i,0} - \delta \sum_{j \neq i} a_{ij}^{(G)} \alpha^{*,j} \right\} \right\}.
	$$
\end{itemize}
\end{remark}


\begin{remark}
In equation \eqref{eq:best_response_player_i},
\begin{itemize}
	\item if $\delta <0$, $br^i$ is increasing in actions of neighbors. We call the game $(A^{1} \times \ldots \times A^{N}, \{J^{i} \}_{i=1,\ldots,N})$ is a game with \textbf{strategic complements}, as the actions chosen by among players mutually reinforce one another.
	\item if $\delta >0$, $br^{i}$ is decreasing in actions of neighbors. We call the game  $(A^{1} \times \ldots \times A^{N}, \{J^{i} \}_{i=1,\ldots,N})$ is a game with \textbf{strategic substitutes}, as the actions chosen among players mutually offset one another.
\end{itemize}
\end{remark}

